19Q2

### 2019-07-10 19Q2.Rmd
update protein changes in G2P db and subsequent analyses--no diff

# Curate protein change column
g2p <- add_column(g2p, Protein_Change = NA, .after = "Mutation")
g2p$Protein_Change <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
g2p$Protein_Change <- ifelse(g2p$Protein_Change == "", str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Protein_Change))
g2p$Protein_Change <- gsub(":| |c\\..*", "", g2p$Protein_Change)
g2p$Protein_Change <- ifelse(!is.na(str_match(string = tolower(g2p$Protein_Change), pattern = "exon|expression|frameshift|fusion|methylation|mutation|-")[,1]), NA, as.character(g2p$Protein_Change))
g2p$Protein_Change <- gsub("^([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Protein_Change)
g2p$Protein_Change <- gsub("^([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Protein_Change)
g2p <- add_column(g2p, Gene_Protein_Change = NA, .after = "Protein_Change")
g2p$Gene_Protein_Change <- ifelse(!is.na(g2p$Gene) & !is.na(g2p$Protein_Change), paste0(as.character(g2p$Gene), ":", as.character(g2p$Protein_Change)), NA)

# Add association columns
g2p[g2p == ""] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p <- merge(lineage_converter, g2p, by = "grouped_general_doid", all.y = TRUE)
g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
g2p$Gene_Lin <- ifelse(is.na(g2p$Drug) | !is.na(g2p$Gene) | !is.na(g2p$group_general_lineage_name), paste0(g2p$Gene, "_", g2p$group_general_lineage_name), NA)

write.csv(g2p, "./data_munging/g2p_db_edited.csv")
```

@@

```{r}
crispr_fus <- readRDS("./data_munging/rds/crispr_fusions.rds")
crispr_prot <- readRDS("./data_munging/rds/crispr_protein_changes.rds")
```

>>>>

# Curate protein change column
g2p <- add_column(g2p, Protein_Change = NA, .after = "Mutation")
g2p <- separate_rows(g2p, Mutation, sep = ",")
g2p$Protein_Change <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
g2p$Protein_Change <- ifelse(g2p$Protein_Change == "", str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Protein_Change))
g2p$Protein_Change <- gsub(":| |c\\..*", "", g2p$Protein_Change)
g2p$Protein_Change <- ifelse(!is.na(str_match(string = tolower(g2p$Protein_Change), pattern = "exon|expression|frameshift|fusion|methylation|mutation|-")[,1]), NA, as.character(g2p$Protein_Change))
g2p$Protein_Change <- gsub("^([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Protein_Change)
g2p$Protein_Change <- gsub("^([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Protein_Change)
g2p <- add_column(g2p, Gene_Protein_Change = NA, .after = "Protein_Change")
g2p$Gene_Protein_Change <- ifelse(!is.na(g2p$Gene) & !is.na(g2p$Protein_Change), paste0(as.character(g2p$Gene), ":", as.character(g2p$Protein_Change)), NA)

# Add association columns
g2p[g2p == ""] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p <- merge(lineage_converter, g2p, by = "grouped_general_doid", all.y = TRUE)
g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
g2p$Gene_Lin <- ifelse(is.na(g2p$Drug) | !is.na(g2p$Gene) | !is.na(g2p$group_general_lineage_name), paste0(g2p$Gene, "_", g2p$group_general_lineage_name), NA)
g2p <- unique(g2p)
write.csv(g2p, "./data_munging/g2p_db_edited.csv")
```

@@

```{r, eval = FALSE}
crispr_fus <- readRDS("./data_munging/rds/crispr_fusions.rds")
crispr_prot <- readRDS("./data_munging/rds/crispr_protein_changes.rds")
```
